True versus apparent shapes of bow shocks

### 2017-11-27 papers/Paper1/sec-thin-shell.tex
Finish making departure function figure for ancantoids
Still need to write about it in text
Finish description in paper of departure function for ancantoids
Add another panel to graph with k=3 and k=8 results

@@

>>>>

\begin{figure}
  \centering
  \setkeys{Gin}{width=\linewidth}
  \begin{tabular}{@{}l@{}}
    (a) \\
    \includegraphics{figs/crw-departure} \\
    (b) \\
    \includegraphics{figs/crw-departure-k38}
  \end{tabular}
  \caption[]{Parabolic departure function, \(\Depart(\cos\theta)\), for
    ancantoids and cantoids.  Heavy lines show the \(\beta = 0\) parallel
    stream case (Wilkinoid in the isotropic case).  Light lines show
    increasing values of \(\beta = \num{e-4}\), \num{0.001}, \num{0.01},
    \num{0.1}, as marked.  (a)~Cantoids (gray) and moderately
    anisotropic ancantoids: hemispheric, \(k = 0\) (black), and
    proplyd-like, \(k = 0.5\) (red). (b)~Cantoids (gray) and extremely
    anisotropic, jet-like ancantoids: \(k = 3\) (purple) and \(k = 8\)
    (blue).}
  \label{fig:ancantoid-departure}
\end{figure}

@@

Figure~\ref{fig:ancantoid-departure} shows the parabolic departure
function (see \S~\ref{sec:parab-depart-funct}) for the thin-shell
models. This provides an alternative perspective on the resultant bow
shapes, with two different types of behavior being apparent.  Models
with high \(\beta\) and low anisotropy behave similarly to the
hyperboloids, such as the
\((\Pi, \Lambda) = (\nicefrac32, \nicefrac83)\), \((2, \nicefrac83)\),
\((\nicefrac83, \nicefrac83)\), and \((\nicefrac32, 2)\) cases from
Figure~\ref{fig:conic-departure}.  This is the case for the
\(\beta \ge 0.01\) models in Figure~\ref{fig:ancantoid-departure}a, which
all show departure functions that become negative in the far wings
(more open than parabola) and terminate at a
\(\theta_\infty < 180^\circ\).  The second type of behavior is shown by models with
low \(\beta\) or high anisotropy, which behave like spheroids for positive
and mildly negative values of \(\cos \theta\), but, unlike the spheroids,
all tend towards \(\Depart = 0\) in the far tail as \(\cos\theta \to -1\).
